A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-19 main.Rmd
done with interval

One of the cornerstones beneath a tsibble is time interval. This information plays a critical role in computing statistics (e.g. seasonal unit root tests) and building models (e.g. seasonal ARIMA). The principal divide is regularly or irregularly spaced in time. Since a tsibble permits implicit missing time, it is impossible to distinguish regularity from the index. It relies on user's specification by switching the `regular` argument off, when the data involves irregular intervals. This type of data can flow into event-based data modelling, not models that expect time series.

As for data indexed in regular time space, the time interval is derived by first computing absolute differences of time indexes and then the greatest common divisor, which covers all conceivable cases. This implies that all subjects in a tsibble have one and the only interval. Data collected at different intervals should be organized in separate tsibbles, encouraging well-tailored analysis and models, because each subject may underly different data generating process.

>>>>

One of the cornerstones of time series data, and hence beneath a tsibble, is the time interval. This information plays a critical role in computing statistics (e.g. seasonal unit root tests) and building models (e.g. seasonal ARIMA). The principal divide is regularly or irregularly spaced observations in time. A tsibble permits implicit missing time, making it  difficult to distinguish regularity from the index. It relies on a user's specification by switching the `regular` argument off, when the data involves irregular intervals. This type of data can flow into event-based data modelling, but would need to be processed or regularized to fit models that expect time series.

For data indexed in regular time space, the time interval is automatically calculated, by first computing absolute differences of time indexes and then the greatest common divisor. This covers all conceivable cases. The implication is that all observations in a tsibble have one and the only interval. Data collected at different intervals should be organized in separate tsibbles, encouraging well-tailored analysis and models, because each observation may  different underlying data generating processes.
